---
title: "Credit Card Clustering"
author: "Tharso Monteiro"
date: "11/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(factoextra)
```

# Loading Data


```{r}
ccdata <- read_csv("CC GENERAL.csv")
```

# EDA

Checking for missing values.

```{r}
dim(ccdata)
```


```{r}
colSums(is.na(ccdata))
```
MINIMUM_PAYMENTS has 313 missing values. CREDIT_LIMIT has 1 missing value.

We will replace these values with the variable median.

```{r}
ccdata$MINIMUM_PAYMENTS[is.na(ccdata$MINIMUM_PAYMENTS)] <- median(ccdata$MINIMUM_PAYMENTS, na.rm = T)
ccdata$CREDIT_LIMIT[is.na(ccdata$CREDIT_LIMIT)] <- median(ccdata$CREDIT_LIMIT, na.rm = T)
```

((Shoud Outliers be removed now??))



# K-means Clustering

We analysed the optimal number of clusters according to within-cluster sum of squared minimization. We see that the scree pĺot stabilizes after the 3rd cluster.

```{r}
ccdata$CUST_ID <- NULL

fviz_nbclust(ccdata, kmeans, method = 'wss')
```

```{r}
cc_km <- kmeans(ccdata,
                3)
```

Vizualising cluters using 2PCs.

```{r}
fviz_cluster(cc_km,
             data = ccdata,
              ellipse = FALSE
             )
```
Interpreting PCs and Clusters.

```{r}
cc_pca <- prcomp(ccdata,
                 center = T,
                 scale = T)
```

```{r}
cc_pca$rotation[,1:2]
```
PC1 : Purchase frequency.
PC2 : Balance and Cash in advance frequency.

We can interpret the clusters as:

1 : Light Credit Card Users
2 : Moderate Credit Card Users
3 : Heavy Credit Card Users

















