---
title: "Hierarchical Clustering"
author: "Tharso Monteiro"
date: "11/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
```

# Hierarchical Clustering


```{r}
econdata <- read_xls('index2021_data.xls')
```

```{r}
glimpse(econdata)
```
Cleaning Data

```{r}
econdata_colnames <- names(econdata)

econdata <- data.frame(lapply(econdata, function(x){
  gsub('N/A',NA,x)
}))

names(econdata) <- econdata_colnames

to_numeric <- function(x){
  as.numeric(as.character(x))
}

econdata <- econdata %>%
  mutate_at(vars(-one_of('Country Name', 'WEBNAME', 'Region', 'Country')),
  to_numeric)

econdata$Country <- NULL
econdata$WEBNAME <- NULL
econdata$CountryID <- NULL
```

```{r}
colSums(is.na(econdata))
```
```{r}
econdata <- econdata %>%
  drop_na()
```


```{r}
econdata$Region <- as_factor(econdata$Region)

econdata <- econdata%>%
  mutate(
    FDI_pop = `FDI Inflow (Millions)`/`Population (Millions)`
  )

econdata$`Region Rank` <- NULL
econdata$`World Rank` <- NULL
econdata$`Population (Millions)` <- NULL
econdata$`FDI Inflow (Millions)` <- NULL
```



Hierarchical Clustering

```{r}
clean_data <- econdata %>%
  select(-one_of("Country Name",'Region'))

clean_data <- apply(clean_data,2,scale)

rownames(clean_data) <- econdata$`Country Name`
```


```{r}
hc_econ <- hclust(dist(clean_data),
                  method = 'complete')
```

```{r}
which(cutree(hc_econ,6)==6)
```

Venezuela is an outlier becuase of 19906.02% inflation. It always creates its own cluster. We will remove it.

```{r}
clean_data <- clean_data[-170,]
```

Doing HC again.

```{r}
hc_econ2 <- hclust(dist(clean_data),
                   method = 'complete')
```

```{r}
table(cutree(hc_econ2,5))
```
```{r}
clean_data <- cbind(clean_data, cluster = c(cutree(hc_econ2,5)))
clean_data <- as.data.frame(clean_data)
```

```{r}
rownames(clean_data[which(clean_data$cluster==1),])
```

```{r}
rownames(clean_data[which(clean_data$cluster==2),])
```
```{r}
rownames(clean_data[which(clean_data$cluster==3),])
```
```{r}
rownames(clean_data[which(clean_data$cluster==4),])
```
```{r}
rownames(clean_data[which(clean_data$cluster==5),])
```


PCA

CONSERTAR : CLUSTER ESTÃ INCLUSO NO PCA

```{r}
pca_econ <- prcomp(clean_data[,-clean_data$cluster])
```

```{r}
pca_df <- data.frame(
  countryname = as.character(rownames(clean_data)),
  PC1 = pca_econ$x[,'PC1'],
  PC2 = pca_econ$x[,'PC2'],
  cluster = factor(clean_data$cluster)
)
```


```{r}
ggplot(pca_df)+
  geom_point(aes(PC1,PC2,colour = cluster))+
  geom_text(aes(PC1,PC2,label = countryname), hjust = 0, vjust = 0)
```

```{r}
pca_econ$rotation
```

* Cluster 1 : Developing and underdeveloped countries
* Cluster 2 : Developed countries which are not global superpowers
* Cluster 3 : Countries in war or severe economical depression
* Cluster 4 : Global superpowers
* Cluster 5 : Louxemburg


